---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RVersatransRP

<!-- badges: start -->
<!-- badges: end -->

The goal of RVersatransRP is to provide easy to use functions for querying and
formatting data from a Versatrans Routing & Planning database.

## Installation

RVersatransRP is currently available from our 
[shared Google Drive folder](https://drive.google.com/drive/folders/1e_C8c5epf8IqcKyP4g9TzaFm1Vnlr8wM?usp=sharing).
I don't think there is any easy way to install or update directly from there, so you
will need to download/sync this shared drive to your local disk and install from there. Once 
you have downloaded/synced the drive directory you can install this package with

``` r
remotes::install_local("path/to/directory")
```

Eventually we will move this package to Github so
you can install the development version of RVersatransRP from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github(".../RVersatransRP")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(RVersatransRP)

student_monitor <- rp_report_student_monitor(database = "Sandbox", format = "long")

## example pickup data:
dplyr::glimpse(
dplyr::select(
  student_monitor,
  -dplyr::contains("ID"), -dplyr::contains("Last"), -dplyr::contains("First")))
```

