---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
if(!knitr::is_html_output()) options(width = 74)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BPSTranspoReportR

<!-- badges: start -->
<!-- badges: end -->

The goal of BPSTranspoReportR is to provide easy to use functions for generating
reports and data summaries from data stored in Versatrans RP/Onscreen, and Zonar.

## Installation

BPSTranspoReportR is currently available from our 
[GitHub page](https://github.com/BostonPublicSchools/BPSTranspoReportR). You can
the development version of BPSTranspoReportR from GitHub with:

``` r
# install.packages("remotes") ## if you don't have remotes installed already
remotes::install_github(c("BostonPublicSchools/RVersatransRP",
                          "BostonPublicSchools/RZonar",
                          "BostonPublicSchools/BPSTranspoReportR")
```

## Example

This is a basic example which shows you how to retrieve the student monitor file
from the Versatrans RP database:

```{r hidden1, echo=FALSE, message=FALSE, warning=FALSE,results='hide'}
devtools::load_all()
tmp <- Sys.Date() -1:-14
tmp <- as.character(tmp)[!weekdays(tmp) %in% c("Saturday", "Sunday")][1]
student_monitor <- otp_report(tmp, ampm="AM", test = TRUE)
```

```{r example1, eval=FALSE}
library(BPSTranspoReportR)

## run report for yesterday
student_monitor <- otp_report(as.character(Sys.Date() -1))
```

```{r}
## OTP data structure:
dplyr::glimpse(student_monitor[0, ])
```

## Credentials and other private information

Usernames, passwords, and other private information will usually be needed in 
order to access the data sources required to generate reports. By default these
are retrieved from environment variables. You can either set these system-wide, 
or set up an `.Renviron` file as described in
https://support.posit.co/hc/en-us/articles/360047157094-Managing-R-with-Rprofile-Renviron-Rprofile-site-Renviron-site-rsession-conf-and-repos-conf.

Note that *this is just for convenience, you can also just pass everything as arguemnts to your function calls*.

If you do set environment variables with private information, 
**make sure that these values are not checked into git or otherwise unintentionally exposed**.

The environment variables consulted by functions in this package are shown in the table below.

| Variable           | Description                                                                  |
| ------------------ | ---------------------------------------------------------------------------- |
| *RP_ODBC_NAME*     | name of the ODBC data source used to connect to Versatrans databases         |
| *RP_DATABASE*      | name of the RP database to use                                               |
| *OS_DATABASE*      | name of the Onscreen database to use                                         |
| *UNCOVERED_URL*    | URL of a google sheet containing uncovered trips list (required)             |
| *MAIL_TO*          | comma separated list of email addresses to send notifications to. (required) |
| *MAIL_FROM*        | gmail address from which notifications should be sent (required)             |
| *TZ*               | time zone, defaults to "America/New_York",                                   |
| *CURL_SSL_BACKEND* | this should always be set to "openssl" (required)                            |
| *ZONAR_CUSTOMER*   | Zonar customer ID (required)                                                 |
| *ZONAR_USER*       | Zonar user name (required)                                                   |
| *ZONAR_PASS*       | ZOnar password (required)                                                    |
| ------------------ | ---------------------------------------------------------------------------- |

